% !TeX spellcheck = en_US 
\chapter{Overview} \label{Overview}


This chapter focuses on the review of the work practiced in this field and the issues associated with the existing forensic investigation systems. It also discusses the purposes, aims and use of a digital forensic investigation system that we will be designing later on. 

Forensic audit is a specialization within a field of accounting that examines and evaluates evidence concerning unproven statements for use as evidence in court. Forensic audit is usually used to investigate the particular crime that has happened. When the exact sequence of events that has led to the crime is investigated and found, it serves as a clear and valid evidence for the hypothesis. The person responsible for the crime is also being searched for, although there is another case when forensic audit is used. This situation occurs when it is not known whether any crime has been committed. Then forensic audit will be conducted to detect, whether in a certain vast company or project any crime has been committed. These case hypotheses are created and then confirmed or disproved according to well examined facts.

Forensic audit therefore deals with assessment of companies or individual's financial data and performance for using it as evidence. It can be used with a specific end goal to investigate the misuse and financial issues of the company. The forensic audits will concentrate on the investigative procedure and its diverse stages to represent them by instinctive methodologies. This bachelor project proposes a design of an information system that can be helpful in one of the stages of forensic audit. 



Digital PC legal forensics that is characterized as expository and investigative strategy is used for safeguarding, proof recognizing, extraction, documentation, investigation and translation of PC media. In this bachelor project we make use of the digital forensics as it provides us the source of information that we display later on. Forensic investigation focus on handling of the criminal cases identified with PCs and systems and also carry out inward corporate examinations and disciplinary inquiries. It may include the obtaining and examination of advanced proof, verification of records, ID of sources and suspects, etc. 


Targeting on a forensic investigation requires going through a few stages. Models of computerized forensics will be described in order to comprehend the logical evidence of the field \cite{3}. As indicated by \cite{4}, such investigation will have an immediate effect on:

\begin{itemize}
\item Anticipation of further malicious instances;
\item Modification of current prevention systems;
\item Enhanced principles for corporate security experts;
\item Expanded consciousness of current vulnerabilities and preventive measures.
\end{itemize}


\section{Review of forensic investigation} 
With the advent of digital revolution in the second half of 90s, the lifestyle of billions of people has changed significantly. In the beginning, all these innovations seemed to be something just to have fun with, but quickly people begun to use the Internet, mobile phones, and other various digital devices in both their professional and personal lives. These technologies have become an indispensable part of everyday life. 

To highlight expectations in this project, we specify here a couple of samples as reviewed in that are specifically identified with our technique of demonstrating. “Pollitt” \cite{3} distinguished four stages in computerized forensic scene investigation, that take after: securing, distinguishing proof, assessment, and affirmation of confirmation, and further portrayed suitability of proof. “The National Institute of Standards and Technology (NIST)” \cite{20} characterizes the fundamental measurable process as following: 

\paragraph{Accumulation:} 
The main stage in the process is to recognize, mark, record, and gain information from the conceivable sources of pertinent information. 

\paragraph{Examination:}
Examinations include forensically preparing a lot of gathered information utilizing a blend of computerized and manual systems to survey and concentrate information specifically compelling. 

\paragraph{Investigation:}
The following period of the procedure is to investigate the consequences of the examination, using legitimately reasonable routines and systems, to infer helpful data that addresses the inquiries that were the impulse for performing the accumulation and examination. 


\paragraph{Reporting:}
The last stage is reporting the consequences of the investigation, which may incorporate depicting the activities utilized, clarifying how devices and methods were chosen, figuring out what different activities should be performed and giving proposals ti change to approaches, rules, techniques, apparatuses, and different parts of the measurable procedure. 

%!!!!CITACE %   Other proposed models incorporate those depicted by Reith, Carr and Gunsch \cite{5}, Carrier and Spafford \cite{6}, Ademu, Imafidon, and Prestonn \cite{8}, and Ciardhuain \cite{7}.


The quantity of different data stored in a digital form is constantly increasing. These data are, for example emails, digital photos, instant messaging history, or phone books.

Our societies have been transforming some traditional crimes, particularly those concerning finance and commerce. For this reason, the importance of an analysis of digital and computer devices has emerged. The field of computer forensic have been created to respond to the needs of the law enforcement and to discover all the digitally stored evidence.

\section{Issues of digital forensic investigation}
As per Tanner and Dampier, digital forensic investigations are turning out to be more unpredictable because of the expanding size of computerized storage. New methodologies for dealing with the digital forensic investigations must be created. In particular, what is needed is to create examination benchmarks and to give structure to PC measurable examinations, furthermore, to capture the tools included in advanced forensic scene investigation \cite{5}.


As indicated by Kohn, Eloff, and Olivier \cite{6}, the majority of the demonstrating representations for measurable examinations found in the present writing  of 2003 are made in a fairly casual and instinctive way". Likewise, "It can be securely said that current models are basically unplanned and should be completed in the specific space" \cite{4}. This bachelor project proposes a conceptual model of the advanced legal strategy taking into account another flow based determination technique that has been used as a part of a few examinations areas.



%\section{Clarification of terms} %upresneni pojmu 

%To clearly understand the issue, it is appropriate to clarify all terms related to the project. 
%Although all of them might not be needed, they are all in a manner associated to the subject, 
%therefore they are worth mentioning.

\subsection{Purpose of forensic audit} 
The purpose of forensic audit is to use accounting procedures to collect evidence for the prosecution or investigation of financial crimes such as theft or fraud. Forensic audits may be conducted to determine if any wrongdoing occurred, or to gather materials for the case against an alleged criminal \cite{x1}.
%Read more: http://www.investorwords.com/16445/forensic_audit.html#ixzz3SFC3Lqlf

%Forensic audit is a specialization within the field of accounting that examines and evaluates evidence concerning unproven statements for use as evidence in court.

Forensic audit is usually used to investigate the particular crime that has happened. In this case the exact sequence of events that has lead to the crime is investigated and when found, it serves as a clear and valid evidence for the hypothesis. The person responsible for the crime is also being searched for. However, there is another case when forensic audit is used. This situation occurs when it is not known whether any crime has been committed. Then forensic audit is conducted to detect whether it is the case or not. These cases usually occur in a vast company or project. In these cases hypotheses are created and then confirmed or disproved according to well examined facts.

\begin{itemize}
\item\textbf{Computer Forensics} is used for investigation of situations where there is a computer-based digital or electronic evidence of a crime or a suspicious behavior. The crime or behavior itself may be of any type not only involving computers.


\item\textbf{Mobile Forensics} is a discipline that primarily analyses mobile applications such as smart phones or GPS navigation systems. 


\item\textbf{Digital Forensics}  is a specialization of forensic science that processes material found in digital devices to support or displace a hypothesis before court.


"It is asserted that digital forensics is a procedure that can be demonstrated with some sensibly settled stages" \cite{4}. Most proposed legal models have concentrated on "the investigative procedure and the distinctive stages that they tend to the quality of an examination and the components and usefulness of tools and the solid standards of an examination.% \cite{5}. ??
\end{itemize}


To highlight expectations in this project, we specify here a couple of examples as reviewed in \cite{3} that are specifically identified with our technique of demonstrating. Pollitt \cite{3} distinguished four stages in computerized forensic scene investigation, that take after: securing, distinguishing proof, assessment, and affirmation of confirmation, and further portrayed suitability of proof. Bearer \cite{1} sketched out layers of deliberation of legal examination where every layer has two inputs and two yields. The National Institute of Standards and Technology (NIST) \cite{3} characterize the fundamental measurable process as following:

\paragraph{Accumulation:} 
The main stage in the process is to recognize, mark, record, and gain information from the conceivable sources of pertinent information. 

\paragraph{Examination:}
Examinations include forensically preparing a lot of gathered information utilizing a blend of computerized and manual systems to survey and concentrate information specifically compelling. 

\paragraph{Investigation:}
The following period of the procedure is to investigate the consequences of the examination, using legitimately reasonable routines and systems, to infer helpful data that addresses the inquiries that were the impulse for performing the accumulation and examination. 


\paragraph{Reporting:}
The last stage is reporting the consequences of the investigation, which may incorporate depicting the activities utilized, clarifying how devices and methods were chosen, figuring out what different activities should be performed and giving proposals ti change to approaches, rules, techniques, apparatuses, and different parts of the measurable procedure. 

Other proposed models incorporate those depicted by Reith, Carr and Gunsch \cite{5}, Carrier and Spafford \cite{6}, Ademu, Imafidon, and Prestonn \cite{8}, and Ciardhuain \cite{7}.

To keep this bachelor project independent, the following segment surveys essential components of the model on which our technique for depicting forensic scene investigation examination is constructed. 

%\todo{} udelat v .ppt  a pridat sem hezky graf ukazujici, jake oblasti spadaji pod 
%forenzni audit a kde se nachazi dalsi terminy

%\section{Project schedule}
%To successfully complete the project it is essential to follow the points below. 
%\begin{itemize}
%\item Evaluate existing programs
%\item Specify requirements of suitable application
%\item Develop our own reasoned and systematic methodology and system design
%\item Develop a system design using UML diagrams
%\item Discuss suitable technology for application development
%\item Summarize
%\end{itemize}



\section{Aims of the project} %cile prace 

The aim of this bachelor project is to design a software application which would help in one of the final stages of the process of forensic audit. The software will be designed to visually demonstrate actions of subjects of the particular case. The design of the software will be described properly.


