% !TeX spellcheck = en_US
\chapter{Analysis}\label{Analysis}

The motivation behind forensic auditing is to devise a system that is not only user friendly and easy to use but also serves the purpose to help auditors with an extensive range of investigation. The work comprises of an investigation in the fiscal matters of a unit and is frequently allied with examinations into suspected deceitful activity.

Forensic auditing covers an extensive range of accomplishments, with terminology not strictly well-defined in the regulatory guidance. Forensic accounting is used to describe the widespread range of investigative exertion that examiners may in practice be requested to implement. The work comprises of an investigation in the fiscal matters of a unit and is frequently allied with examinations into suspected deceitful activity. Forensic accounting analyzes the whole procedure of investigating a fiscal matter, together with hypothetically acting as an expert spectator if the fraud comes to court of justice. 

Though this bachelor project concentrates on investigations into suspected frauds, it is essential to be aware that the forensic accountants may be asked to consider also non-fraud circumstances.
%, like resolving of financial disputes relative to a business termination or matrimonial clashes under insurance claims.

The procedure of forensic accounting analyses as designated above contains the forensic investigation itself, which indicates the practical phases that the forensic accountant undertakes in order to collect evidence pertinent to the suspected deceitful activity. The investigation is expected to be related in many means to an audit of financial evidence, in that it must contain a development phase, a period when proof is collected, an appraisal procedure, and a specific report to the user. The ambition of the investigation, in the matter of a suspected fraud, will be to determine if a deception had truly taken place in order to classify those involved, to enumerate the fiscal expanse of the deception i.e. the monetary cost by the user, and to eventually present the outcomes to the client and possibly to the court. 


Finally, forensic auditing deals with precise procedures approved to create evidence. Audit procedures are used to classify and to gather proof of, for example, how long ago the fraud has been carried out, and how it was handled and covered by the perpetrators. Proof is gathered to support other matters that would be pertinent in the occasion of a lawsuit. 

Such matters could consist of: 
\begin{itemize}
\item the defendant's motivation and convenience to commit the fraud 
\item to see if the fraud contained collusion among certain defendants
\item any physical proof at the area of the crime or included in the documents 
\item remarks made by the examiner throughout interviews and at the moment of arresting 
\item efforts to abolish evidence.
\end{itemize}

\section{Types of investigation}

The forensic auditor could be demanded to examine various sorts of fraud. To analyze the extensive area of examinations that could be completed, these sorts of fraud can be classified into three categories. The first category containing frauds such as conflict of interest, extortion or bribery. Approximately one third of fraudulent activities is somehow connected to corruption.In the second category we can find acts of cash theft, fraudulent disbursement or misuse of assets. This category can be generally called asset misappropriation and activities related to it are actually the most common frauds. All financial statement frauds may be considered as the third separate category, including all the deliberate misinterpretation of financial reporting standards or manipulation with obligations to improve analyses of liquidity. 



\subsection{Asset misappropriation}
Clearly the most widely recognized frauds are those including resource misappropriations and there are various sorts of misrepresentation which fall into this classification. The basic element is the burglary of money or different resources from the organization, for instance: 

\begin{itemize}
\item Cash burglary – the taking of physical money, for instance insignificant amount of money, from the premises of an organization.
\item Fraudulent payment – organization trusts being utilized to make fake installments. Regular illustrations incorporate charging plans where installments are made to an imaginary supplier and finance plans where installments are made to invented workers that are frequently known as 'apparition representatives'.
\item Inventory replicas – the robbery of stock from the organization. 
\item Misuse of benefits – representatives utilizing organization resources for their own interest.
\end{itemize}


\subsection{Financial statement fraud}

This is deceitful money related reporting, and is a kind of misrepresentation that causes a material misquote in the budgetary proclamations. It can incorporate planned distortion of bookkeeping records; exclusion of exchanges, equalizations or exposures from the budgetary explanations; or the misuse of money-related reporting guidelines. This is regularly done with the goal of giving the budgetary proclamations a specific inclination, for instance covering liabilities to enhance any examination of liquidity.


\section{Conducting the investigation}

The procedure of directing a forensic examination is, from various perspectives, like the procedure of leading a review, however, with some extra contemplation. The different stages are precisely discussed below.

\subsection{Accepting the investigation}

The forensic accountant will at first contemplate whether the firm has essential aptitudes and knowledge to acknowledge the work. As forensic examinations are professional in nature, and the work entails definite learning of misrepresentation examination strategies and legitimate system, agents should likewise prepare meetings and cross examination systems, and consider how to keep up the secure upkeep of proof accumulated.

Extra contemplations incorporate regardless of whether the examination is being asked for by a review customer. In the event that it is, this suggests additional moral conversation starters, as the examining firm would be possibly be presented to self-audit, promotion and administration risks to objectivity . Unless strong shields are set up, the firm ought not to give review and measurable examination administrations to the same client. Business contemplations are additionally critical and a high charge level ought to be arranged to make up for the way of the work and the conceivable contribution of senior and experienced individuals from the firm in the examination.


\subsection {Planning the investigation}

The examining group should precisely contemplate what they are requested to accomplish and arrange their work consequently. The purpose of this examination will include: 

\begin{itemize}
\item Identifying the sort of misrepresentation that has been working, to what extent it has been working to, and how the work has been hidden.
\item Identifying the fraud(s) included.
\item Quantifying the budgetary trouble endured by the ordering party.
\item Gathering confirmation to be utilized as a part of court procedures. 
\item Providing advice to avoid the fraud to be repeated.
\end{itemize}


The agents ought to additionally consider the most ideal approach to assemble proof i.e. the utilization of PC assisted review procedures, for instance, it is exceptionally regular in extortion examinations.

\subsection{Gathering proof}

To assemble the proofs, the forensic auditor must comprehend what particular sort of fraud that has happened, and how it has been accomplished. The evidence ought to be strong and adequate enough to eventually identify the fraudsters, their plan of accomplishing the fraud and, and the sum of money lost due to the fraud. It is essential that forensic auditors are talented in gathering proof that is usable proof in a trial, and in keeping the evidence hidden until it is displayed in court. If any proof is uncertain, then it may be called into question in court, or even be forbidden. 

Forensic auditors must be aware that some of the material may be falsified on purpose, impaired or ruined by the suspect(s).

\section{Summary of Investigation techniques}

A forensic examination tends to be an extremely expert kind of engagement, which requires highly talented individuals who have knowledge of audit methods, technology and also law. 

There are various diverse kinds of fraud that a forensic auditor could be requested to research. The examination tends to eventually prompt legitimate procedures against one or a few individuals.

Forensic auditors must be prepared to demonstrate at the court how the examination has been  performed and how the proofs have been gathered. Forensic auditors should therefore get expert training in such matters to guarantee that their credibility and polished skill can't be undermined in the time of the legitimate procedure. To become familiar with the present circumstances, examinations of tools that are being used as a part of the procedure of forensic audit have been performed. 


\begin{itemize}
\item{Tools used in investigation:}
%\begin{itemize}
%\item Public Databases \cite{10}
%\item Secretary of State Websites
%\item Country Seat
%\item Corporate Records
%\item Internet
%\end{itemize}

\begin{itemize}
\item{Public Databases \cite{10}}
\begin{itemize}
\item Increasing number of vendors
\item Reliability of data
\item What type of data is available?
\end{itemize}

\item{Internet}
\begin{itemize}
\item Search Engines \cite{10}
\item News Sources/Newspapers
\item Telephone Numbers and Addresses
\item Maps
\item Legal Resources
\item Government Sites \cite{10}
\item Computer Forensics
\begin{itemize}
\item hard disk imaging
\item E-mail analysis
\item search for erased files
\item analyze use \& possible misuse
\item computer software to analyze data \cite{10}
\end{itemize}
\end{itemize}

\item{Physical}
\begin{itemize}
\item usually done by law enforcement or PI's
\item surveillance cameras
\item can also be used to verify addresses for vendors, employees, etc. \cite{10}
\end{itemize}


\item{Electronic}
\begin{itemize}
\item Internet surveillance
\item E-mail \cite{10}
\end{itemize}
\end{itemize}
\end{itemize}


Obtaining information from equipment may require diverse systems relying upon information state and the numerous conceivable stockpiling structures. 

PC media drives such as RAM, CDs, DVD and Mobile gadgets including telephones, PDAs, iPods, GPS Network Infrastructure, printers, servers, O/S, Active Directory (AD),  databases, Cloud, Apple, iCloud, MobileMe, Amazon S3, Google and cloud storage all analyze the conditions of the equipment and information before communicating.


In a perfect world equipment ought to be gathered "in-state" and transported to secured, "flawless" environment for investigation. Obtained equipment requires approval for fulfillment and accuracy like information acceptance.


%\todo %vyjadrit se k otazce pocitacove podpory konkretnich fazi prosetrovani... (splnit zadani BP)

%
%To get to know the current situation an investigation of programs that are being used in the 
%process of forensic audit have been performed. Although the original idea, what the perfect 
%forensic-audit tool should look like is quite simple, (it should be just one tool that does 
%everything) the reality is entirely different. There \todo {is a lot of} tools that can be used 
%for a great number of situations one can get into while conducting a forensic audit 
%investigation. Moreover, in each specific situation, there is also a variety of associated 
%technical parameters and technical parameter values, that, in fact, often answer the question, 
%whether an initial problem has its solution in using one or another tool. 

\section{Existing software}

The existing software in the market is either inefficient in terms of results or does not full fill the requirements for conducting proper evaluation. For this reason, Computer Forensic Tool Catalog has been created as an effective way of connecting practitioners to the tools they need. This catalog is available on the "National Institute of Standards and Technology" web pages \cite{10}. The information about forensic functionalities and associated technical parameters and their values can be provided by any vendor, in order to be integrated to the database. All tools are being reviewed before posting. This catalog can be considered rich in the database and it is also systematic and searchable. The only problem is it is not possible to select free tools only. This catalog can be recommended to any practitioner as a useful instrument for choosing suitable software for their situation. Although other lists of software can be found browsing the Internet, this one is reliable and provides the possibility of search in the tools according to technological needs.

The functionalities of the tools contained in the catalog are mostly usable in one of the first stages of forensic audit. This stage could also be called preparatory stage because the auditor is preparing background for the search for evidence. Documents and all possibly available data related to the studied case are being collected. Depending on the character of the case, data from various pieces of hardware can be collected. In some situations, if the tool is sophisticated enough, the following analysis of the data can be performed immediately within the same tool.

The functionality choices in the Computer Forensics Tool Catalog \cite{20}:

\begin{itemize}
\item Cloud Services
\item Deleted File Recovery
\item Disk Imaging
\item Email Parsing
\item File Carving
\item Forensics Boot Environment
\item Forensic Tool Suite (Mac Investigations)
\item Forensic Tool Suite (Windows Investigations)
\item GPS Forensics
\item Hardware Write Block
\item Hash Analysis
\item Image Analysis (Graphics Files)
\item Infotainment and Vehicle Forensics
\item Instant Messenger
\item Media Sanitization/Drive Re-use
\item Memory Capture and Analysis
\item Mobile Device Acquisition, Analysis and Triage
\item P2P Analysis
\item Password Recovery
\item Remote Capabilities / Remote Forensics
\item Social Media
\item Software Write Block
\item Steganalysis
\item String Search
\item Web Browser Forensics
\item Windows Registry Analysis
\end{itemize}



The work of the auditor usually starts by getting to know the situation because each case has its specific character. After that they need to collect all the hardware that holds important data and extract all the data stored in these devices. According to the type of device they may use proper software that is good for acquisition of the data stored.


%//pridat tabulku reprezentujici: platformy, cena, funkce(), specifika, reprezentace dat, jak moc jsou bezne vyuzivane

\section{Software analysis}
\paragraph{Quantative software}\label{qSW}

Specialized fraud identifying software is making a passage into the business, with extortion module discharges from both ACL and IDEA\textsuperscript{\textregistered}, extortion parts in SAS and SPSS, and a devoted extortion discovery program in Picalo. Programming organizations like ACL and IDEA\textsuperscript{\textregistered} give exercise manuals that can be utilized as a part of courses, however, these exercise manuals have couple of illustrations of direct misrepresentation recognition particularly with cutting edge procedures. Approaches like the theory testing methodology are an initial phase in giving procedure research, immense extra research—both observational and field—are expected to approve and augment the current ideas.

Quantative software organizations give complete preparing on measurable programming and systems. The two driving programming bundles are EnCase by Guidance Software and the Forensic Toolkit (FTK) by Access Data . These suites give shorter expectations to absorb information than past utilities and convey a more prominent number of experts to the field more rapidly. Both bundles give tasks positioned procedures to securing and illustrating forensic information.


Lately, Linux based apparatuses have been prevalent as free distinct options for the conventional suites. Helix, the Penguin Sleuth, and Security Tools Distribution are Linux dispersions that run specifically from CD, giving clean situations to seeking a PC without the requirement for cloning (Causey, 2005). These instruments boot a suspect PC straightforwardly to Linux and mount the client hard drives in read just mode, basically bypassing most passwords and security insurances. While Linux based instruments are more hard to use and do not have the same point of reference in court as EnCase and FTK, they have to be well known with a few evaluators.


%TODO: poradne popsat qSW

\paragraph{The R Project for Statistical Computing} 
R is mathematical software specialized in statistics. It concerns an open-source implementation of the S language, which is used by other professional statistical applications. It is a good choice in case that great amount of data needs to be processed because R is suited for large data sets.
%\cite{http://www.r-project.org/about.html}


\paragraph{Using SAS to evaluate risks }

Measurable packages like SAS and SPSS give full drifting modules to the intrigued inspector. Statement on Auditing Standards (SAS) and consideration of fraud in a financial statement audit requires inspectors to evaluate the risk that misrepresentation might physically misquote budgetary articulations. Regardless of SAS 99 being an imperative necessity towards expanded misrepresentation, a study by "Marczewski and Akers"\cite{21} uncovered that Certified Public Accountants (CPAs) do not envision that SAS 99 will generously expand review viability. Another study found that while SAS 99 expanded examiner obligation, most reviewers experienced issues recognizing the work and its risks.



\paragraph{SPSS for statistical and analytical services}

SPSS is one of the leading analytical instruments. It provides statistical and analytical services the abbreviation originally meant Statistical Package for the Social Sciences. This software supports areas of social survey and market research, predictive and advanced analytics, decision management and deployment or predictive solutions.

%\cite{http://www-01.ibm.com/common/ssi/cgi-bin/ssialias?infotype=PM&subtype=BR&appname=SWGE_YT_YV_USEN&htmlfid=YTB03015USEN&attachment=YTB03015USEN.PDF}

\paragraph{COFEE}
Useful tools for basic forensics are Microsoft's COFEE tools. They are a set of PC forensic and evaluating tools that Microsoft puts on a USB key and provides for law requirement. It is used in attempting to concentrate information from a PC. There was some apprehension that it was an "indirect access", however, individuals demanded it was no such thing, yet only a gathering of essential tools. Still, the this framework was advanced as being valuable for decoding passwords and examining a PC's information and web action that appeared to be alarming. If Microsoft was giving it out to law requirement, it appeared to be likely that others would have entry to it also.


%doplnit!
\paragraph{IDEA\textsuperscript{\textregistered}}
IDEA\textsuperscript{\textregistered} is an effective and easy to understand information investigation tool intended to help reviewers; bookkeepers and other account experts perform information examination rapidly to help enhance reviews and distinguish control breakdowns. It permits to dissect 100\% of the information to ensure information trustworthiness and gives simple investigation more that 100 major studied activities. 

At the point when the information originates from distinctive sources and in a mixed bag of configurations, information investigation can infrequently be a test. The capacity to import different information sets and represents it as if they were one that lets us to see the master plan. We have the capacity to recognize connections, examples and inconsistencies and additionally direct a far reaching examination of value-based information. 

Import Data from Practically Any Source IDEA\textsuperscript{\textregistered} permits us to rapidly import a boundless measure of records from for all intents and purposes of any source, including spreadsheet and \textbf{database programming}, mid-extent bookkeeping projects, ERP frameworks, legacy centralized servers, telecommunication switches, travel and costs applications, level and printed documents, for example, PDFs, plain content (.txt), and print-report (.prn) records. Rearranged analysis instead of programming macros can use more than 100 review particular undertakings that easily search for copies, identify dumps in numeric groupings, group information by classes and channel various lines and sections of data in seconds. IDEA\textsuperscript{\textregistered} permits us to record each investigative step and reuse for future utilization, through a graphical interchange and customized interface. 

\paragraph{Microsoft Analytics Services}
Procedures utilized for misrepresentation discovery fall into two essential classes: factual systems and computerized reasoning. Examples of measurable information examination methods are: 

\begin{itemize}
\item Data preprocessing strategies for discovery, acceptance, slip adjustment, and topping of missing or off base information.
\item Calculation of different factual parameters, for example, midpoints, quintiles, execution measurements, lihelihood circulations. For instance the midpoints may incorporate normal length of call, normal number of calls every month and normal defers in bill installment.
\item Models and likelihood dispersions of different business exercises either regarding different parameters or likelihood circulations.
\item Computing client profiles.
\item Time-arrangement investigation of time-ward information.
\item Clustering and grouping to discover examples and relationship among gatherings of information.
\item Matching calculations to recognize abnormalities in the conduct of exchanges or clients when contrasted with already known models and profiles. Methods are likewise expected to dispose of false alerts, assessment chances, and foresee eventual fate of current exchanges or clients. % \todo cite.
\end{itemize}

Some measurable bookkeepers work in criminological investigation which is the acquisition and examination of electronic information to reproduce, distinguish, or generally bolster a case of monetary misrepresentation. The fundamental strides in criminological examination are (a) information gathering, (b) information planning, (c) information investigation, and (d) reporting \cite{16}.Case in point, forensic examination may be utilized to audit a representative's obtaining card action on evaluate whether any of the purchases were occupied or divertible for individual utilization. Forensic examination may be utilized to survey the invoicing action for merchant to distinguish imaginary sellers, and these systems may likewise be utilized by franchisor to recognize deceitful or mistaken deals reports by the franchise in a franchising situation.

In the next step the reviewer needs to process picked up information to have capacity to some criminological bookkeepers and spend significant time in legal investigation which is the acquisition and examination of electronic information to remake, distinguish, or generally bolster a case of budgetary extortion. The principle ventures in legal investigation are (a) information gathering, (b) information arrangement, (c) information examination, and (d) reporting. For instance, legal examination may be utilised to survey a worker's buying card action to evaluate whether any of the buys were occupied or divertible for individual utilization. 

Customary strategies for information investigation have long been utilized to identify misrepresentation. They require complex and time intensive examination that arrange with diverse spaces of learning like budgetary, financial matters, business practices and law. Misinterpretation regularly comprises of numerous occurrence or incidents including rehashed transgressions utilizing the same technique.


\section {Conclusion of the analysis}

In order to create efficient evaluation software it must be created with significant measure of basic knowledge and have the capacity to perform intelligent task including learning and the information given. Therefore to meet this objective, analysis have swung to idea from machine learning field. As intelligent systems branched out from machine learning it helps forecasting trends based upon the previous data and can make decisions on its own. In the event that data mining results in finding significant examples, information transforms into data. Data or examples that are novel, substantial and conceivably valuable are not just data, but rather information. One discussion about finding information before covered up in the enormous measure of information, however, now it is exposed. 

%To go past, an information examination framework must be furnished with a significant measure of foundation learning, and have the capacity to perform thinking errands including learning and the information given. In push to meet this objective, analysts have swung to thoughts form machine learning field. This is a characteristic wellspring of thoughts, since the machine learning undertaking can be depicted as turning foundation of information and cases (info) and learning (yield).
%
%In the event that information mining results in finding significant examples, information transforms into data. Data or examples that are novel, substantial and concievably valuable are not just data, but rather information, before coveded up in the enormous measure of information, however, now will be made visible. 

